---
title: "Regressions - The increasing association between child poverty and out-of-home care - longitudinal ecological analysis of Finnish municipalities in 1992-2021"
format: html
editor: visual
code-fold: true
always_allow_html: true
---

```{r}
#| echo: false
#| output: false
library(magrittr) #
library(tidyverse) #
library(modelsummary)
library(estimatr)
library(lme4)
#library(ggpubr)
library(here)

#clearing memory
#rm(list=ls())


```

## Regression models

-   Model 1: all years pooled without municipality fixed effects

-   Model 2: 1992 - 2001 ---""\--

-   Model 3: 2002 - 2011 ---""\--

-   Model 4: 2012 - 2021 ---""\--

-   Model 5: all years pooled with municipality fixed effects

-   Model 6: 1992 - 2001 ---""\--

-   Model 7: 1992 - 2001 ---""\--

-   Model 8: 1992 - 2001 ---""\--

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models. The Frist three models are without municipality fixed effects. "

dsw.d <- readRDS(here("data", "processed", "data_imputed.rds"))
teens <- readRDS(here("data", "processed", "data_imputed_teens.rds"))

#model.data <- filter(dsw.d, region.class == "KUNTA" & gender == "total")
all.years <- filter(dsw.d, region.class == "KUNTA" & gender == "total")
Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))

datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

lmrobust <- function(dataset) {
  lm_robust(ohc ~ poverty + unemp + factor(year), clusters = region, data = dataset)
}

within <- function(dataset) {
  lm_robust(ohc ~ poverty + unemp + factor(year), clusters = region, data = dataset, fixed_effects = ~ region)

}

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - lagged variable

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models. The Frist three models are without municipality fixed effects. "
library(Hmisc)

all.years <- filter(dsw.d, region.class == "KUNTA" & gender == "total")

data_lag <- all.years %>% 
  group_by(region) %>% 
  dplyr::mutate(poverty_lag = Lag(as.numeric(poverty),+1)) %>% 
  ungroup

#model.data <- filter(dsw.d, region.class == "KUNTA" & gender == "total")
Years.1992.01 <- filter(data_lag, year %in% (1992:2001))
Years.2002.11 <- filter(data_lag, year %in% (2002:2011))
Years.2012.21 <- filter(data_lag, year %in% (2012:2021))

datasets <- list(data_lag, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)


within_lag <- function(dataset) {
  lm_robust(ohc ~ poverty_lag + unemp + factor(year), clusters = region, data = dataset, fixed_effects = ~ region)

}

results2 <- purrr::map(datasets,within_lag)

results <-c(results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - female

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models."

#model.data <- filter(dsw.d, region.class == "KUNTA" & gender == "female")

all.years <- filter(dsw.d, region.class == "KUNTA" & gender == "female")
Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))
datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - male

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models."

#model.data <- filter(dsw.d, region.class == "KUNTA" & gender == "male")

all.years <- filter(dsw.d, region.class == "KUNTA" & gender == "male")
Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))
datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - preteenagers

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models."
teens_kunta <- filter(teens, region.class == "KUNTA")

all.years <- filter(teens_kunta, region.class == "KUNTA" & gender == "total" & age.group == "Ages 0 - 12")
all.years$ohc<- all.years$ohc_age

Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))
datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - teenagers

```{r}
#| warning: false 
#| tbl-cap: "Association between child poverty and out-of-home care in Finnish municipalities. Linear models."
all.years <- filter(teens_kunta, region.class == "KUNTA" & gender == "total" & age.group == "Ages 13 - 17")
all.years$ohc<- all.years$ohc_age

#write.dta(model.data, "C:/Users/HIILAMO/Downloads/mydata.dta")

Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))
datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")

```

## Regression models - larger geographical units

```{r}
#| label: gif_MAAKUNTA
#| fig-cap: Child poverty rate (5 of families with social assistance) in Finnish municipalities between 1992 and 2020.
#| warning: false 
#| eval: true

all.years <- filter(dsw.d, region.class == "MAAKUNTA" & gender == "total")
Years.1992.01 <- filter(all.years, year %in% (1992:2001))
Years.2002.11 <- filter(all.years, year %in% (2002:2011))
Years.2012.21 <- filter(all.years, year %in% (2012:2021))
datasets <- list(all.years, 
          Years.1992.01,
          Years.2002.11,
          Years.2012.21)

results1 <- purrr::map(datasets,lmrobust)
results2 <- purrr::map(datasets,within)

results <-c(results1,results2)
modelsummary(
  results, gof_map = c("nobs", "r.squared"),
  fmt = 0,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "factor*|Intercept|region*|unemp*", 
  notes = "Models include years as factor and unemployment rate")


```
